Biomarker screening

### 2022-04-27 code/r/01_MSDW_HPO_Phenotype_Analysis.Rmd
update analysis

@@

ggsave(filename = glue('{CACHE_DIR}/plot_by_sex.png'), plot = plot_by_sex, width = 2.5, height = 2.5)
ggsave(filename = glue('{CACHE_DIR}/plot_by_sex.pdf'), plot = plot_by_sex, width = 2.5, height = 2.5)
plot_by_sex
```

@@

ggsave(filename = glue("{CACHE_DIR}/plotByRace.png"), plot = plot_by_race, width = 5, height = 2)
ggsave(filename = glue("{CACHE_DIR}/plotByRace.pdf"), plot = plot_by_race, width = 5, height = 2)
plot_by_race
```
Fraction of each race:
```{r}
countByRace_Gender %>% 
  group_by(race) %>% 
  summarise(n = sum(n)) %>%
  mutate(fraction = n / sum(n)) %>% 
  arrange(desc(fraction))
```

@@

ggsave(filename = glue("{CACHE_DIR}/plotByBirthyearSex.png"), plot = plot_by_birth_year_sex, width = 4, height = 3)
ggsave(filename = glue("{CACHE_DIR}/plotByBirthyearSex.pdf"), plot = plot_by_birth_year_sex, width = 4, height = 3)
plot_by_birth_year_sex
```

@@

Plot the distribution of distinct phenotypes for each patient (including abnormal and abnormal)
```{r}
plot_by_phenotypes_per_patient <- ggplot(hpo_counts_per_patient) +
  geom_histogram(aes(x = n_distinct_hpo, y = ..count../1000), binwidth = 10, fill = 'orange', color = 'black', size = 0.25) +
  xlab('number of unique phenotypes for each patient') +
  ylab('patient counts (in thousands)') + 
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title = element_text(size = 8), axis.text = element_text(size = 8), 
        legend.text = element_text(size = 8), legend.title = element_text(size = 10))
ggsave(filename = glue("{CACHE_DIR}/plotByPhenotypesPerPatient.png"), plot = plot_by_phenotypes_per_patient, width = 3, height = 2)
plot_by_phenotypes_per_patient
```
Plot distribution of abnormal phenotypes (distinct) after inference
```{r}
plot_by_distinct_abnormal_hpo_infer_per_patient <- ggplot(hpo_counts_per_patient) +
  geom_histogram(aes(x = n_distinct_abnormal_hpo_infer, y = ..count../1000), binwidth = 10, fill = 'orange', color = 'black', size = 0.25) +
  xlab('number of unique phenotypes for each patient') +
  ylab('patient counts (in thousands)') + 
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title = element_text(size = 8), axis.text = element_text(size = 8), 
        legend.text = element_text(size = 8), legend.title = element_text(size = 10))
ggsave(filename = glue("{CACHE_DIR}/plotByDistinctAbnormalPhenotypeInferPerPatient.png"), plot = plot_by_distinct_abnormal_hpo_infer_per_patient, width = 3, height = 2)
plot_by_distinct_abnormal_hpo_infer_per_patient
```

@@

```{r}
patient_lab_phenotype_journeys_formated <- patient_lab_phenotype_journeys %>% 
  filter(medical_record_number == '7611233') %>% 
  select(-medical_record_number) %>% 
  group_by(lab_year, isnegated) %>% 
  slice_head(n = 5) %>% 
  mutate(display = glue('{hpotermid} {label} ({n} times)')) %>% 
  summarise(display = str_c(display, collapse = '\n'), .groups = 'drop')
write.csv(patient_lab_phenotype_journeys_formated, file = glue('{CACHE_DIR}/patient_lab_phenotype_journey_formatted.csv'))
```

@@

hpo_level_1_terms <- phenotype_rank_all_by_year %>% filter(distancetoroot == 1) %>% select(termid, label) %>% distinct()
p <- plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df=phenotype_rank_all_by_year, normalize = FALSE)
ggsave(filename = glue('{CACHE_DIR}/plot_abnormal_phenotypes_by_year_level_1.pdf'), plot = p, width = 8, height = 4)
p
```

```{r}
hpo_level_1_terms <- phenotype_rank_all_by_year %>% filter(distancetoroot == 1) %>% select(termid, label) %>% distinct()
p <- plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df= phenotype_rank_all_by_year %>%
                                           left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year'), normalize = TRUE)
ggsave(filename = glue('{CACHE_DIR}/plot_abnormal_phenotypes_by_year_level_1_normalized.pdf'), plot = p, width = 8, height = 4)
p
```

@@

write.csv(trendline_lm_test_formatted, file = glue('{CACHE_DIR}/table_abnormal_phenotypes_by_year_level_1_normalized_trendline_lm_model.csv'), row.names=FALSE)

@@

```{r}
hpo_level_1_terms <- tested_phenotype_rank_all_by_year %>% filter(distancetoroot == 1) %>% select(termid, label) %>% distinct()
p <- plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df=tested_phenotype_rank_all_by_year, normalize = FALSE)
ggsave(filename = glue('{CACHE_DIR}/plot_tested_phenotypes_by_year_level_1.pdf'), plot = p, width = 8, height = 4)
p
```
```{r}
p <- plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df=tested_phenotype_rank_all_by_year %>% left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year'), normalize = TRUE)
ggsave(filename = glue('{CACHE_DIR}/plot_tested_phenotypes_by_year_level_1_normalized.pdf'), plot = p, width = 8, height = 4)
p
```

@@

write.csv(trendline_lm_test_formatted, file = glue('{CACHE_DIR}/table_tested_phenotypes_by_year_level_1_normalized_trendline_lm_model.csv'), row.names=FALSE)

@@

write.csv(racial_abnormality_fisher, file = glue('{CACHE_DIR}/racial_abnormality_fisher.csv'), row.names = FALSE)

@@

ggsave(filename = glue('{CACHE_DIR}/plot_by_phenotype_racial_difference_over_years.pdf'), plot = p, width = 8, height = 8)

@@

write.csv(racial_tested_abnormality_fisher, file = glue('{CACHE_DIR}/racial_tested_abnormality_fisher.csv'), row.names = FALSE)

@@

ggsave(filename = glue('{CACHE_DIR}/plot_by_tested_phenotype_racial_difference_over_years.pdf'), plot = p, width = 8, height = 8)

@@

write.csv(overly_tested_abnormalities_by_each_race_top10, file=glue('{CACHE_DIR}/overly_tested_abnormalities_by_each_race_top10.csv'), row.names = FALSE)

overly_tested_abnormalities_by_each_race_top10 %>% 
  ungroup() %>% 
  #filter(race == 'Asian') %>% 
  rename(OR = median_OR) %>% 
  rename(`Lab Record` = lab_record) %>% 
  rename(`Patient Count` = patient_count) %>% 
  mutate(OR = round(OR, digits = 3)) %>%
  group_by(race) %>% 
  nest() %>% {
    walk2(.$race, .$data, 
          function(race_name, df) sjPlot::tab_df(df, 
                                                 alternate.rows = TRUE, 
                                                 title = glue("Top 10 Overly Tested Lab Phenotype for {race_name}"), 
                                                 use.viewer = FALSE, 
                                                 file = glue('{CACHE_DIR}/table_overly_tested_abnormalities_for_{race_name}_top10.html')))
  }

@@

  sjPlot::tab_df(df, alternate.rows = TRUE, 
                     title = glue("Top 10 Overly Tested Lab Phenotype for {race_name}: 2003 - 2019"), 
                 footnote = 'OR: odds of having received lab tests for the phenotype in the race vs other races; <br>
                phenotypes with less than 1700 tested patients were excluded',
                 show.footnote = TRUE,
                     use.viewer = FALSE, 
                     file = glue('{CACHE_DIR}/table_overly_tested_abnormalities_for_{race_name}_top10.html'))
}
table_overly_tested_by_race(race_name = 'Asian')
table_overly_tested_by_race(race_name = 'Black or African American')
table_overly_tested_by_race(race_name = 'White')
```

>>>>

OUT_DIR = '../../out'
if (!dir.exists(OUT_DIR)){
  dir.create(OUT_DIR)
}

@@

ggsave2(filenames = c(glue('{OUT_DIR}/plot_by_sex.png'), glue('{OUT_DIR}/plot_by_sex.pdf')), plot = plot_by_sex, width = 2.5, height = 2.5)
plot_by_sex
```

@@

ggsave2(filenames = c(glue("{OUT_DIR}/plotByRace.png"), glue("{OUT_DIR}/plotByRace.pdf")), plot = plot_by_race, width = 5, height = 2)
plot_by_race
```
Fraction of each race:
```{r}
countByRace_Gender %>% 
  group_by(race) %>% 
  summarise(n = sum(n)) %>%
  mutate(fraction = n / sum(n)) %>% 
  arrange(desc(fraction))
```

@@

ggsave2(filenames = c(glue("{OUT_DIR}/plotByBirthyearSex.png"), glue("{OUT_DIR}/plotByBirthyearSex.pdf")), plot = plot_by_birth_year_sex, width = 4, height = 3)
plot_by_birth_year_sex
```

@@

Plot the distribution of distinct phenotypes for each patient (including abnormal and abnormal)
```{r}
plot_by_phenotypes_per_patient <- ggplot(hpo_counts_per_patient) +
  geom_histogram(aes(x = n_distinct_hpo, y = ..count../1000), binwidth = 10, fill = 'orange', color = 'black', size = 0.25) +
  xlab('number of unique phenotypes for each patient') +
  ylab('patient counts (in thousands)') + 
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title = element_text(size = 8), axis.text = element_text(size = 8), 
        legend.text = element_text(size = 8), legend.title = element_text(size = 10))
ggsave2(filenames = c(glue("{OUT_DIR}/plotByPhenotypesPerPatient.png"), glue("{OUT_DIR}/plotByPhenotypesPerPatient.pdf")), plot = plot_by_phenotypes_per_patient, width = 3, height = 2)
plot_by_phenotypes_per_patient
```
Plot distribution of abnormal phenotypes (distinct) after inference
```{r}
plot_by_distinct_abnormal_hpo_infer_per_patient <- ggplot(hpo_counts_per_patient) +
  geom_histogram(aes(x = n_distinct_abnormal_hpo_infer, y = ..count../1000), binwidth = 10, fill = 'orange', color = 'black', size = 0.25) +
  xlab('number of unique phenotypes for each patient') +
  ylab('patient counts (in thousands)') + 
  theme_bw() +
  theme(panel.grid = element_blank(),
        axis.title = element_text(size = 8), axis.text = element_text(size = 8), 
        legend.text = element_text(size = 8), legend.title = element_text(size = 10))
ggsave2(filenames = c(glue("{OUT_DIR}/plotByDistinctAbnormalPhenotypeInferPerPatient.png"), glue("{OUT_DIR}/plotByDistinctAbnormalPhenotypeInferPerPatient.pdf")), plot = plot_by_distinct_abnormal_hpo_infer_per_patient, width = 3, height = 2)
plot_by_distinct_abnormal_hpo_infer_per_patient
```

@@

```{r}
patient_lab_phenotype_journeys_formated <- patient_lab_phenotype_journeys %>% 
  filter(medical_record_number == '7611233') %>% 
  select(-medical_record_number) %>% 
  group_by(lab_year, isnegated) %>% 
  slice_head(n = 5) %>% 
  mutate(display = glue('{hpotermid} {label} ({n} times)')) %>% 
  summarise(display = str_c(display, collapse = '\n'), .groups = 'drop')
write.csv(patient_lab_phenotype_journeys_formated, file = glue('{OUT_DIR}/patient_lab_phenotype_journey_formatted.csv'))
```

@@

hpo_level_1_terms <- phenotype_rank_all_by_year %>% filter(distancetoroot == 1) %>% select(termid, label) %>% distinct()
p <- plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df=phenotype_rank_all_by_year, normalize = FALSE)
ggsave2(filenames = c(glue('{OUT_DIR}/plot_abnormal_phenotypes_by_year_level_1.png'), glue('{OUT_DIR}/plot_abnormal_phenotypes_by_year_level_1.pdf')), plot = p, width = 8, height = 4)
p
```

```{r}
hpo_level_1_terms <- phenotype_rank_all_by_year %>% filter(distancetoroot == 1) %>% select(termid, label) %>% distinct()
p <- plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df= phenotype_rank_all_by_year %>%
                                           left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year'), normalize = TRUE)
ggsave2(filenames = c(glue('{OUT_DIR}/plot_abnormal_phenotypes_by_year_level_1_normalized.png'), glue('{OUT_DIR}/plot_abnormal_phenotypes_by_year_level_1_normalized.pdf')), plot = p, width = 8, height = 4)
p
```

@@

write.csv(trendline_lm_test_formatted, file = glue('{OUT_DIR}/table_abnormal_phenotypes_by_year_level_1_normalized_trendline_lm_model.csv'), row.names=FALSE)

@@

```{r}
hpo_level_1_terms <- tested_phenotype_rank_all_by_year %>% filter(distancetoroot == 1) %>% select(termid, label) %>% distinct()
p <- plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df=tested_phenotype_rank_all_by_year, normalize = FALSE)
ggsave2(filenames = c(glue('{OUT_DIR}/plot_tested_phenotypes_by_year_level_1.png'), glue('{OUT_DIR}/plot_tested_phenotypes_by_year_level_1.pdf')), plot = p, width = 8, height = 4)
p
```
```{r}
p <- plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df=tested_phenotype_rank_all_by_year %>% left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year'), normalize = TRUE)
ggsave2(filenames = c(glue('{OUT_DIR}/plot_tested_phenotypes_by_year_level_1_normalized.png'), glue('{OUT_DIR}/plot_tested_phenotypes_by_year_level_1_normalized.pdf')), plot = p, width = 8, height = 4)
p
```

@@

write.csv(trendline_lm_test_formatted, file = glue('{OUT_DIR}/table_tested_phenotypes_by_year_level_1_normalized_trendline_lm_model.csv'), row.names=FALSE)

@@

write.csv(racial_abnormality_fisher, file = glue('{OUT_DIR}/racial_abnormality_fisher.csv'), row.names = FALSE)

@@

ggsave2(filenames = c(glue('{OUT_DIR}/plot_by_phenotype_racial_difference_over_years.png'), glue('{OUT_DIR}/plot_by_phenotype_racial_difference_over_years.pdf')), plot = p, width = 8, height = 8)

@@

write.csv(racial_tested_abnormality_fisher, file = glue('{OUT_DIR}/racial_tested_abnormality_fisher.csv'), row.names = FALSE)

@@

ggsave2(filenames = c(glue('{OUT_DIR}/plot_by_tested_phenotype_racial_difference_over_years.png'), glue('{OUT_DIR}/plot_by_tested_phenotype_racial_difference_over_years.pdf')), plot = p, width = 8, height = 8)

@@

write.csv(overly_tested_abnormalities_by_each_race_top10, file=glue('{OUT_DIR}/overly_tested_abnormalities_by_each_race_top10.csv'), row.names = FALSE)

overly_tested_abnormalities_by_each_race_top10 %>% 
  ungroup() %>% 
  #filter(race == 'Asian') %>% 
  rename(OR = median_OR) %>% 
  rename(`Lab Record` = lab_record) %>% 
  rename(`Patient Count` = patient_count) %>% 
  mutate(OR = round(OR, digits = 3)) %>%
  group_by(race) %>% 
  nest() %>% {
    walk2(.$race, .$data, 
          function(race_name, df) sjPlot::tab_df(df, 
                                                 alternate.rows = TRUE, 
                                                 title = glue("Top 10 Overly Tested Lab Phenotype for {race_name}"), 
                                                 use.viewer = FALSE, 
                                                 file = glue('{OUT_DIR}/table_overly_tested_abnormalities_for_{race_name}_top10.html')))
  }

@@

  sjPlot::tab_df(df, alternate.rows = TRUE, 
                     title = glue("Top 10 Overly Tested Lab Phenotype for {race_name}: 2003 - 2019"), 
                 footnote = 'OR: odds of having received lab tests for the phenotype in the race vs other races; <br>
                phenotypes with less than 1700 tested patients were excluded',
                 show.footnote = TRUE,
                     use.viewer = FALSE, 
                     file = glue('{OUT_DIR}/table_overly_tested_abnormalities_for_{race_name}_top10.html'))
}
table_overly_tested_by_race(race_name = 'Asian')
table_overly_tested_by_race(race_name = 'Black or African American')
table_overly_tested_by_race(race_name = 'White')
```

### 2022-04-27 code/r/02_A_numeric_vs_hpo_for_liver_function.Rmd
update analysis

# cache directory to read from or write to
CACHE_DIR = '../../cache'
if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}
FORCE_RERUN <- FALSE
```

@@

ggsave(filename = glue('{CACHE_DIR}/liver_labs_raw_data_distribution_by_rel_date.png', plot = p, width = 6, height = 6))
```

@@

write.csv(liver_analysis, file = glue('{CACHE_DIR}/liver_analysis.csv'), row.names = FALSE)

>>>>

# cache directory to read from or write to
CACHE_DIR = '../../cache'
if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}

# output directory to write analysis results
OUT_DIR = '../../out'
if (!dir.exists(OUT_DIR)){
  dir.create(OUT_DIR)
}

# if true, ignore cached data and reconnect to database to get latest data;
# otherwise, use cached data first before trying to connect to database
FORCE_RERUN <- FALSE
```

@@

ggsave2(filenames = c(glue('{OUT_DIR}/liver_labs_raw_data_distribution_by_rel_date.png'), glue('{OUT_DIR}/liver_labs_raw_data_distribution_by_rel_date.pdf')), plot = p, width = 6, height = 6)
```

@@

write.csv(liver_analysis, file = glue('{OUT_DIR}/liver_analysis.csv'), row.names = FALSE)

### 2022-04-27 code/r/02_B_numeric_vs_hpo_for_acute_kidney_failure.Rmd
update analysis

if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}
FORCE_RERUN <- FALSE
```

@@

ggsave(filename = 'cache/kidney_labs_raw_data_distribution_by_rel_date.png', plot = p, width = 6, height = 6)
```

![liver function labs](./cache/kidney_labs_raw_data_distribution_by_rel_date.png)

@@

write.csv(kidney_analysis, file = 'cache/acute_kidney_failure_analysis.csv', row.names = FALSE)

>>>>

if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}

# output directory to write analysis results
OUT_DIR = '../../out'
if (!dir.exists(OUT_DIR)){
  dir.create(OUT_DIR)
}

# if true, ignore cached data and reconnect to database to get latest data;
# otherwise, use cached data first before trying to connect to database
FORCE_RERUN <- FALSE
```

@@

ggsave2(filenames = c(glue('{OUT_DIR}/kidney_labs_raw_data_distribution_by_rel_date.png'), glue('{OUT_DIR}/kidney_labs_raw_data_distribution_by_rel_date.pdf')), plot = p, width = 6, height = 6)
```

![liver function labs](./../../out/kidney_labs_raw_data_distribution_by_rel_date.png)

@@

write.csv(kidney_analysis, file = glue('{OUT_DIR}/acute_kidney_failure_analysis.csv'), row.names = FALSE)

### 2022-04-27 code/r/02_C_numeric_vs_hpo_for_blood_disorder.Rmd
update analysis

## Goal
Compare the performance of raw lab values vs HPO interpretations for seme blood disorders

@@

FORCE_RERUN <- FALSE
```

@@

ggsave(filename = 'cache/anemia_labs_raw_data_distribution_by_rel_date.png', plot = p, width = 5, height = 5)
```

![liver function labs](./cache/anemia_labs_raw_data_distribution_by_rel_date.png)

@@

write.csv(anemia_analysis, file = 'cache/anemia_analysis.csv', row.names = FALSE)

>>>>

## Goal
Compare the performance of raw lab values vs HPO interpretations for some blood disorders

@@

# output directory to write analysis results
OUT_DIR = '../../out'
if (!dir.exists(OUT_DIR)){
  dir.create(OUT_DIR)
}

# if true, ignore cached data and reconnect to database to get latest data;
# otherwise, use cached data first before trying to connect to database
FORCE_RERUN <- FALSE
```

@@

ggsave2(filenames = c(glue('{OUT_DIR}/anemia_labs_raw_data_distribution_by_rel_date.png'), glue('{OUT_DIR}/anemia_labs_raw_data_distribution_by_rel_date.pdf')), plot = p, width = 5, height = 5)
```

![liver function labs](./../../out/anemia_labs_raw_data_distribution_by_rel_date.png)

@@

write.csv(anemia_analysis, file = glue('{OUT_DIR}/anemia_analysis.csv'), row.names = FALSE)

### 2022-04-27 code/r/02_E_numeric_vs_hpo_combined.Rmd
update analysis

# cache directory to read from or write to
CACHE_DIR = '../../cache'
```

Load previous data analysis results
```{r}
liver_analysis <- read.csv(glue('{CACHE_DIR}/liver_analysis.csv'))
crc_analysis <- read.csv(glue('{CACHE_DIR}/crc_case_matched_controls_analysis.csv'))
acute_kidney_failure_analysis <- read.csv(glue('{CACHE_DIR}/acute_kidney_failure_analysis.csv'))
anemia_analysis <- read.csv(glue('{CACHE_DIR}/anemia_analysis.csv'))
```

@@

plot_AUC_differences_numeric_vs_hpo <- ggplot(df, aes(x = method, y = auc, group = interaction(disease, loinc))) + 
  geom_point(size = 1) +
  geom_line(aes(color = disease)) +
  scale_x_discrete(breaks = c('continuous', 'hpo'), labels = c('original numeric value', 'transformed to HPO')) +
  xlab("Use Lab Test Results As") +
  ylab("AUC") +
  theme_bw() + 
    theme(panel.grid = element_blank(), legend.position = 'none',
          axis.text = element_text(size = 8),
          axis.title = element_text(size = 8), 
          strip.text.x = element_text(margin = margin(0.3, 0, 0.3, 0), size = 8),
          plot.title = element_text(size = 8)) +
  facet_wrap(~ disease)

ggsave(filename = glue('{CACHE_DIR}/plot_AUC_differences_numeric_vs_hpo.pdf'), width = 6, height = 5)

>>>>

source('functions.R')

# cache directory to read from or write to
CACHE_DIR = '../../cache'

# output directory to write analysis results
OUT_DIR = '../../out'
if (!dir.exists(OUT_DIR)){
  dir.create(OUT_DIR)
}

```

Load previous data analysis results
```{r}
liver_analysis <- read.csv(glue('{OUT_DIR}/liver_analysis.csv'))
crc_analysis <- read.csv(glue('{OUT_DIR}/crc_case_matched_controls_analysis.csv'))
acute_kidney_failure_analysis <- read.csv(glue('{OUT_DIR}/acute_kidney_failure_analysis.csv'))
anemia_analysis <- read.csv(glue('{OUT_DIR}/anemia_analysis.csv'))
```

@@

plot_AUC_differences_numeric_vs_hpo <- ggplot(df, aes(x = method, y = auc, group = interaction(disease, loinc))) + 
  geom_point(size = 1) +
  geom_line(aes(color = disease)) +
  scale_x_discrete(breaks = c('continuous', 'hpo'), labels = c('numeric', 'HPO')) +
  xlab("Use Lab Test Results As") +
  ylab("AUC") +
  theme_bw() + 
    theme(panel.grid = element_blank(), legend.position = 'none',
          axis.text = element_text(size = 8),
          axis.title = element_text(size = 8), 
          strip.text.x = element_text(margin = margin(0.3, 0, 0.3, 0), size = 8),
          plot.title = element_text(size = 8)) +
  facet_wrap(~ disease)

ggsave2(filenames = c(glue('{OUT_DIR}/plot_AUC_differences_numeric_vs_hpo.png'), glue('{OUT_DIR}/plot_AUC_differences_numeric_vs_hpo.pdf')), plot = plot_AUC_differences_numeric_vs_hpo, width = 3.2, height = 3.2)

### 2022-04-27 code/r/03_A_biomarker.Rmd
update analysis

# cache directory to read from or write to
CACHE_DIR = '../../cache'

if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}
FORCE_RERUN <- TRUE
```

>>>>

# cache directory to read from or write to
CACHE_DIR = '../../cache'
if (!dir.exists(CACHE_DIR)){
  dir.create(CACHE_DIR)
}

# if true, ignore cached data and reconnect to database to get latest data;
# otherwise, use cached data first before trying to connect to database
FORCE_RERUN <- FALSE
```
